publications

### 2022-02-24 index.Rmd
check github
update photo

---
title: "Sam Parsons"
image: "SamProfile.jpg"
preview: "SamProfile.jpg"
twitter:
  site: "@sam_d_parsons"
links:
  - label: '<i class="fab fa-twitter"></i> Twitter'
    url: "https://twitter.com/sam_d_parsons"
  - label: '<i class="fab fa-github"></i> GitHub'
    url: "https://github.com/sdparsons"
  - label: '<i class="fas fa-envelope"></i> Email'
    url: "mailto:sam.parsons@radboudumc.nl"
  - label: '<i class="ai ai-orcid"></i> ORCID'
    url: "https://orcid.org/0000-0002-7048-4093"
  - label: '<i class="ai ai-publons"></i> Publons'
    url: "https://publons.com/researcher/1351322/sam-parsons/"
  - label: '<i class="fab fa-youtube"></i> YouTube'
    url: "https://www.youtube.com/channel/UC3C_BRgKQNqZH2P2R5U2cfw"
  - label: '<i class="ai ai-osf"></i> OSF'
    url: "https://osf.io/k7akr/"
  - label: '<i class="ai ai-cv"></i> CV'
    url: "Sam_Parsons_cv.pdf"
output: 
  postcards::jolla
site: distill::distill_website
---

@@

**About me** I’m a [Radboud Excellence Initiative](https://www.ru.nl/excellence/) Postdoctoral Research Fellow. I work in the [Lifespan Cognitive Dynamics Lab](https://www.rogierkievit.com/) based at the [Donders Institute](https://www.ru.nl/donders/). I did my DPhil in Experimental Psychology at the University of Oxford^[a DPhil is a PhD but of course they need to call it something else]

Just in case you’re here for the cat, this ginger monster is called Beau.

>>>>

---
title: "Sam Parsons"
image: "SP_Profile.jpg"
preview: "SP_Profile.jpg"
twitter:
  site: "@sam_d_parsons"
links:
  - label: '<i class="fab fa-twitter"></i> Twitter'
    url: "https://twitter.com/sam_d_parsons"
  - label: '<i class="fab fa-github"></i> GitHub'
    url: "https://github.com/sdparsons"
  - label: '<i class="fas fa-envelope"></i> Email'
    url: "mailto:sam.parsons@radboudumc.nl"
  - label: '<i class="ai ai-orcid"></i> ORCID'
    url: "https://orcid.org/0000-0002-7048-4093"
  - label: '<i class="ai ai-publons"></i> Publons'
    url: "https://publons.com/researcher/1351322/sam-parsons/"
  - label: '<i class="fab fa-youtube"></i> YouTube'
    url: "https://www.youtube.com/channel/UC3C_BRgKQNqZH2P2R5U2cfw"
  - label: '<i class="ai ai-osf"></i> OSF'
    url: "https://osf.io/k7akr/"
  - label: '<i class="ai ai-cv"></i> CV'
    url: "Sam_Parsons_cv.pdf"
output: 
  postcards::jolla
site: distill::distill_website
---

@@

**About me** I am a [Radboud Excellence Initiative](https://www.ru.nl/excellence/) Postdoctoral Research Fellow. I work in the [Lifespan Cognitive Dynamics Lab](https://www.rogierkievit.com/) based at the [Donders Institute](https://www.ru.nl/donders/). I did my DPhil in Experimental Psychology at the University of Oxford^[a DPhil is a PhD but of course they need to call it something else]

### 2022-02-24 papers.Rmd
update photo

@@

@@

Lim, M. C., **Parsons, S.**, Goglio, A., Fox, E. (2021). Anxiety, stress, and binge eating behaviours in adolescence: a prospective approach. *Journal of Eating Disorders, 9*. [doi.org/10.1186/s40337-021-00444-2](https://doi.org/10.1186/s40337-021-00444-2)

@@

**Parsons, S** (2020). Exploring reliability heterogeneity with multiverse analyses: Data processing decisions unpredictably influence measurement reliability. Under review at Meta-Psychology. Preprint: [psyarxiv.com/y6tcz](https:/psyarxiv.com/y6tcz), data and code: [osf.io/haz6u/](https://osf.io/haz6u/)

>>>>

(please note: I will add pdfs links asap)

@@

### 2022

Azevedo, F., Lui, M., Pennington, C., Pownall, M., Evans, T., **Parsons, S.**, Elsherif, M., Micheli, L., Westwood, S., & Framework for Open and Reproducible Research Training (FORRT). (2022). Towards a culture of open scholarship: the role of pedagogical communities. *BMC Research Notes, 15*, 75. [doi.org/10.1186/s13104-022-05944-1](https://doi.org/10.1186/s13104-022-05944-1)

<aside>
<div data-badge-type="donut" data-doi="10.1186/s13104-022-05944-1" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

**Parsons, S.**, Azevedo, F., Elsherif, M. M. M., Guay, S., ... & Aczel, B. (2022) A Community-Sourced Glossary of Open Scholarship Terms. *Nature Human Behavior*. [doi.org/10.1038/s41562-021-01269-4](https://doi.org/10.1038/s41562-021-01269-4). preprint: [osf.io/preprints/metaarxiv/kdqcw](https://osf.io/preprints/metaarxiv/kdqcw). Open access link: [rdcu.be/cHsqM](rdcu.be/cHsqM). website: [forrt.org/glossary/](https://forrt.org/glossary/)

<aside>
<div data-badge-type="donut" data-doi="10.1038/s41562-021-01269-4" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

**Parsons, S.**, Todorovic, A., Lim, M., Songco, A., & Fox, E. (2022). Data and protocol for the Oxford Achieving Resilience during COVID-19 (ARC) study. *accepted for publication in the Journal of Open Psychology Data*

**Parsons, S** (2020). Exploring reliability heterogeneity with multiverse analyses: Data processing decisions unpredictably influence measurement reliability. *accepted for publication at Meta-Psychology*. Preprint: [psyarxiv.com/y6tcz](https:/psyarxiv.com/y6tcz), data and code: [osf.io/haz6u/](https://osf.io/haz6u/)

@@

Pownall, M., Azevedo, F., Aldoh, A., Elsherif, M. Vasilev, M., Pennington, C., Robertson, O., Vel Tromp, M., Lui, M., Makel, M., Tonge, N., Moreau, D., Horry, R., Shaw, J., Tzavella, L., McGarrigle, R., Talbot, C., **Parsons, S.*, & FORRT (2021). Embedding open and reproducible science into teaching: A bank of lesson plans and resources.  *Scholarship of Teaching and Learning in Psychology*. [doi.org/10.1037/stl0000307](https://doi.org/10.1037/stl0000307)

<aside>
<div data-badge-type="donut" data-doi="10.1037/stl0000307" data-hide-no-mentions="true" class="altmetric-embed"></div>
<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>
</aside>

Lim, M. C., **Parsons, S.**, Goglio, A., & Fox, E. (2021). Anxiety, stress, and binge eating behaviours in adolescence: a prospective approach. *Journal of Eating Disorders, 9*. [doi.org/10.1186/s40337-021-00444-2](https://doi.org/10.1186/s40337-021-00444-2)

@@
